\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{CAS 741: Problem Statement\\ Scientific Data Processing}

\author{Malavika Srinivasan and sriniva}

\date{Sep 15, 2018}

\input{../Comments}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sep 15, 2018 & Malavika Srinivasan & Problem statement creation\\
Sep 17, 2018 & Spencer Smith & Corrections in problem statement\\
Sep 18, 2018 & Malavika Srinivasan & 
Changes made in problem statement for corrections mentioned on Sep 17, 2018.\\
Sep 19, 2018& Spencer Smith & Changes suggested on Sep 19, 2018. \\
Sep 24, 2018& Malavika Srinivasan & Changes made for corrections on Sep 19, 2018. \\
\bottomrule
\end{tabularx}
\end{table}

Scientific Computation (SC) is the collection of tools, techniques, and theories
that are required to solve problems in the field of science and engineering
using computer-based mathematical models. The source data for scientific
computation problems are often large sets of data from experiments conducted in
a laboratory setup. This large set of data (such as time and temperature) is
usually complex to analyze and require segmenting and curve-fitting.

The purpose of this software family is to develop a general purpose library for
fitting the experimental data using a 1D function to enable simpler data
processing. In other words, the software is intended to be used as a tool to fit
the data and compute derivatives. In this software, regression and interpolation
are the two techniques used for data fitting.

Interested stakeholders in this project may include researchers in industrial
and academic set-up, students, technicians and those who deal with processing of
a large set of data to obtain critical information within a dataset. The
processing encoded into the current software will be suitable for any scientific
application which will require scientific data processing like obtaining a fit
for the data, interpolating across the domain and computing derivatives. This
software can be run on a variety of personal desktop and laptop computers using
Linux, Windows, or MacOS.


%Put your problem statement here.  Comments to you can be added, like this:

%\wss{comment}

%You can also leave comments for yourself, like this:

%\an{comment}

\end{document}